---
title: "Digital_Index"
format: html
editor: visual
---

# Municipality digitalization and local engagement: The case of Chile

Pedro Fierro, Ellen Helsper, Teresa Correa and Matias Dodel

## Loading Packages

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
rm(list=ls())

library(haven)
library(tidyverse)
library(sf)
library(spdep)
library(foreign)
library(car)
library(broom)
library(interactions)
library(tigris)
library(corrplot)
library(ggthemes)
library(patchwork)
library(showtext)
library(scico)
library(sjPlot)
library(ggsci)
library(readxl)
library(stringi)
library(stringr)
library(lavaan)
library(psych)
library(rdrobust)
library(lmtest)
library(sandwich)
library(clubSandwich)

```


## Data at the municipal level

### Loading Data, Shapefiles and Merging

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
shape <- st_read("map_chile.shp")
data_sinim <- read_excel("Data_Mun_2023.xlsx", col_names = TRUE)
data_index <- read_excel("Data_Digital_Index.xlsx", col_names = TRUE)

shape <- shape %>%
  select(CUTCOM, CUTPROV, CUTREG, NOMBRE, Superficie, geometry)

data_sinim$Comuna <- data_sinim$Comuna %>%
  stri_replace_all_fixed("ñ", "N") %>%  # Replace ñ with N
  stri_trans_general("Latin-ASCII")      # Remove accents

data_sinim$Pob_Rural_Porc <- data_sinim$Pob_Rural/100
data_sinim <- data_sinim %>%
  mutate(log_Ingresos_Propios_Permanentes = ifelse(Ingresos_Propios_Permanentes > 0,
                                                   log(Ingresos_Propios_Permanentes), 
                                                   NA))
data_sinim <- data_sinim %>%
  mutate(log_Num_Planta_Profes = ifelse(Num_Planta_Profes > 0,
                                                   log(Num_Planta_Profes), 
                                                   NA))

data_sinim <- data_sinim %>%
  mutate(share_Planta_Profes = ifelse(Num_Planta_Profes > 0 & Num_Planta > 0,
                                       Num_Planta_Profes / Num_Planta, 
                                       NA))

data_sinim <- data_sinim %>%
  mutate(log_Poblacion.y = ifelse(Poblacion > 0,
                                          log(Poblacion), 
                                          NA))

shape <- shape %>%
  mutate(log_Superficie = ifelse(Superficie > 0,
                                          log(Superficie), 
                                          NA))

# Apply the transformation to the 'comuna' column in the dataset
data_index <- data_index %>%
  mutate(Comuna = stri_trans_general(str_to_upper(Comuna), "Latin-ASCII"))

data_index <- data_index %>%
  mutate(Comuna = ifelse(Comuna == "TAITAL", "TALTAL",
                         ifelse(Comuna == "TIL TIL", "TILTIL",
                                ifelse(Comuna == "MACHALLI", "MACHALI",
                                       ifelse(Comuna == "COYHAIQUE", "COIHAIQUE",
                                              ifelse(Comuna == "PAIHUANO", "PAIGUANO", Comuna))))))
      

# Check the first few rows to verify
head(data_index)
data_index$NOMBRE <- data_index$Comuna
merged_data <- left_join(shape, data_index, by = "NOMBRE")
merged_data <- left_join(merged_data, data_sinim, by = "Comuna")

merged_data$Ingresos_Propios_Permanentes <- as.numeric(merged_data$Ingresos_Propios_Permanentes)


md_north <- merged_data %>%
  filter(CUTREG %in% c("01", "02", "03", "04", "15"))

md_centre <- merged_data %>%
  filter(CUTREG %in% c("05", "06", "07", "13"))

md_south <- merged_data %>%
  filter(CUTREG %in% c("08", "09", "10", "11" , "12", "14", "16"))


```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Find cases in data_index that could not find a match in map_data
unmatched_cases <- anti_join(data_index, shape, by = "NOMBRE")

# View the first few rows of the unmatched cases
head(unmatched_cases)
```

## Loading fonts and theme for maps and graphs

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# load font
font_add_google("Roboto Condensed", "robotocondensed")
# automatically use showtext to render text
showtext_auto()

theme_map <- function(...) {
  theme_tufte() +
  theme(
    text = element_text(family = "robotocondensed", size = 30),
    strip.text = element_text(size = 30),
    # legend
    legend.title=element_text(size=20), 
    legend.text=element_text(size=18),
    # remove all axes
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    legend.position = "right"
    )
}

theme_tufte2 <- function(...) {
  theme_tufte() +
  theme(
    text = element_text(family = "robotocondensed", size = 24),
    )
}

```

## Data at the Individual-Level
### Loading data and creating contextual variables

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
EOP <- read_dta("digital_data.dta")

EOP$mun_id <- max.col(EOP[, c("com1", "com2", "com3", "com4", "com5", 
                                         "com6", "com7", "com8", "com9", "com10")])


EOP <- EOP %>%
  mutate(dig_mun = case_when(
    com1 == 1 ~ 0.607, #LosAndes
    com2 == 1 ~ 0.440, #LaLigua
    com3 == 1 ~ 0.645, #Quillota
    com4 == 1 ~ 0.475, #SanAntonio
    com5 == 1 ~ 0.610,   #SanFelipe
    com6 == 1 ~ 0.528,  #Concon
    com7 == 1 ~ 0.769, #Valparaiso
    com8 == 1 ~ 0.743,   #VinaDelMar
    com9 == 1 ~ 0.716,  #Quilpue
    com10 == 1 ~ 0.599, #VillaAlemana
    TRUE ~ NA_real_
  ))

EOP <- EOP %>%
  mutate(dig_mun_2 = case_when(
    com1 == 1 ~ merged_data %>% filter(Comuna == "LOS ANDES") %>% pull(Municipio_Digital),  # LosAndes
    com2 == 1 ~ merged_data %>% filter(Comuna == "LA LIGUA") %>% pull(Municipio_Digital),   # LaLigua
    com3 == 1 ~ merged_data %>% filter(Comuna == "QUILLOTA") %>% pull(Municipio_Digital),   # Quillota
    com4 == 1 ~ merged_data %>% filter(Comuna == "SAN ANTONIO") %>% pull(Municipio_Digital), # SanAntonio
    com5 == 1 ~ merged_data %>% filter(Comuna == "SAN FELIPE") %>% pull(Municipio_Digital),  # SanFelipe
    com6 == 1 ~ merged_data %>% filter(Comuna == "CONCON") %>% pull(Municipio_Digital),     # Concon
    com7 == 1 ~ merged_data %>% filter(Comuna == "VALPARAISO") %>% pull(Municipio_Digital), # Valparaiso
    com8 == 1 ~ merged_data %>% filter(Comuna == "VINA DEL MAR") %>% pull(Municipio_Digital), # VinaDelMar
    com9 == 1 ~ merged_data %>% filter(Comuna == "QUILPUE") %>% pull(Municipio_Digital),    # Quilpue
    com10 == 1 ~ merged_data %>% filter(Comuna == "VILLA ALEMANA") %>% pull(Municipio_Digital), # VillaAlemana
    TRUE ~ NA_real_
  ))


EOP <- EOP %>%
  mutate(popul = case_when(
    com1 == 1 ~ merged_data %>% filter(Comuna == "LOS ANDES") %>% pull(log_Poblacion.y),  # LosAndes
    com2 == 1 ~ merged_data %>% filter(Comuna == "LA LIGUA") %>% pull(log_Poblacion.y),   # LaLigua
    com3 == 1 ~ merged_data %>% filter(Comuna == "QUILLOTA") %>% pull(log_Poblacion.y),   # Quillota
    com4 == 1 ~ merged_data %>% filter(Comuna == "SAN ANTONIO") %>% pull(log_Poblacion.y), # SanAntonio
    com5 == 1 ~ merged_data %>% filter(Comuna == "SAN FELIPE") %>% pull(log_Poblacion.y),  # SanFelipe
    com6 == 1 ~ merged_data %>% filter(Comuna == "CONCON") %>% pull(log_Poblacion.y),     # Concon
    com7 == 1 ~ merged_data %>% filter(Comuna == "VALPARAISO") %>% pull(log_Poblacion.y), # Valparaiso
    com8 == 1 ~ merged_data %>% filter(Comuna == "VINA DEL MAR") %>% pull(log_Poblacion.y), # VinaDelMar
    com9 == 1 ~ merged_data %>% filter(Comuna == "QUILPUE") %>% pull(log_Poblacion.y),    # Quilpue
    com10 == 1 ~ merged_data %>% filter(Comuna == "VILLA ALEMANA") %>% pull(log_Poblacion.y), # VillaAlemana
    TRUE ~ NA_real_
  ))

EOP <- EOP %>%
  mutate(ingresos = case_when(
    com1 == 1 ~ merged_data %>% filter(Comuna == "LOS ANDES") %>% pull(log_Ingresos_Propios_Permanentes),  # LosAndes
    com2 == 1 ~ merged_data %>% filter(Comuna == "LA LIGUA") %>% pull(log_Ingresos_Propios_Permanentes),   # LaLigua
    com3 == 1 ~ merged_data %>% filter(Comuna == "QUILLOTA") %>% pull(log_Ingresos_Propios_Permanentes),   # Quillota
    com4 == 1 ~ merged_data %>% filter(Comuna == "SAN ANTONIO") %>% pull(log_Ingresos_Propios_Permanentes), # SanAntonio
    com5 == 1 ~ merged_data %>% filter(Comuna == "SAN FELIPE") %>% pull(log_Ingresos_Propios_Permanentes),  # SanFelipe
    com6 == 1 ~ merged_data %>% filter(Comuna == "CONCON") %>% pull(log_Ingresos_Propios_Permanentes),     # Concon
    com7 == 1 ~ merged_data %>% filter(Comuna == "VALPARAISO") %>% pull(log_Ingresos_Propios_Permanentes), # Valparaiso
    com8 == 1 ~ merged_data %>% filter(Comuna == "VINA DEL MAR") %>% pull(log_Ingresos_Propios_Permanentes), # VinaDelMar
    com9 == 1 ~ merged_data %>% filter(Comuna == "QUILPUE") %>% pull(log_Ingresos_Propios_Permanentes),    # Quilpue
    com10 == 1 ~ merged_data %>% filter(Comuna == "VILLA ALEMANA") %>% pull(log_Ingresos_Propios_Permanentes), # VillaAlemana
    TRUE ~ NA_real_
  ))


EOP <- EOP %>%
  mutate(ingresos_real = case_when(
    # Los Andes (com1)
    com1 == 1 & year == 2018 ~ 4645895,
    com1 == 1 & year == 2019 ~ 4865905,
    com1 == 1 & year == 2020 ~ 4604735,
    com1 == 1 & year == 2021 ~ 5155003,
    com1 == 1 & year == 2022 ~ 5612060,
    com1 == 1 & year == 2023 ~ 6451780,

    # La Ligua (com2)
    com2 == 1 & year == 2018 ~ 2071141,
    com2 == 1 & year == 2019 ~ 2383557,
    com2 == 1 & year == 2020 ~ 2054672,
    com2 == 1 & year == 2021 ~ 2298635,
    com2 == 1 & year == 2022 ~ 3099116,
    com2 == 1 & year == 2023 ~ 3446070,

    # Quillota (com3)
    com3 == 1 & year == 2018 ~ 5332847,
    com3 == 1 & year == 2019 ~ 5700325,
    com3 == 1 & year == 2020 ~ 5847935,
    com3 == 1 & year == 2021 ~ 6116414,
    com3 == 1 & year == 2022 ~ 7347986,
    com3 == 1 & year == 2023 ~ 8793033,

    # San Antonio (com4)
    com4 == 1 & year == 2018 ~ 8487794,
    com4 == 1 & year == 2019 ~ 8337983,
    com4 == 1 & year == 2020 ~ 7432215,
    com4 == 1 & year == 2021 ~ 7678088,
    com4 == 1 & year == 2022 ~ 9474049,
    com4 == 1 & year == 2023 ~ 11403479,

    # San Felipe (com5)
    com5 == 1 & year == 2018 ~ 4985728,
    com5 == 1 & year == 2019 ~ 4916318,
    com5 == 1 & year == 2020 ~ 4734414,
    com5 == 1 & year == 2021 ~ 4979189,
    com5 == 1 & year == 2022 ~ 5324025,
    com5 == 1 & year == 2023 ~ 6717066,

    # Concón (com6)
    com6 == 1 & year == 2018 ~ 8500485,
    com6 == 1 & year == 2019 ~ 10203493,
    com6 == 1 & year == 2020 ~ 8411017,
    com6 == 1 & year == 2021 ~ 9678668,
    com6 == 1 & year == 2022 ~ 11953057,
    com6 == 1 & year == 2023 ~ 14266237,

    # Valparaíso (com7)
    com7 == 1 & year == 2018 ~ 25738609,
    com7 == 1 & year == 2019 ~ 25427132,
    com7 == 1 & year == 2020 ~ 22965174,
    com7 == 1 & year == 2021 ~ 24386015,
    com7 == 1 & year == 2022 ~ 28396394,
    com7 == 1 & year == 2023 ~ 31659119,

    # Viña del Mar (com8)
    com8 == 1 & year == 2018 ~ 78202635,
    com8 == 1 & year == 2019 ~ 72661171,
    com8 == 1 & year == 2020 ~ 52210264,
    com8 == 1 & year == 2021 ~ 63139305,
    com8 == 1 & year == 2022 ~ 83985932,
    com8 == 1 & year == 2023 ~ 97734155,

    # Quilpué (com9)
    com9 == 1 & year == 2018 ~ 8369150,
    com9 == 1 & year == 2019 ~ 8678205,
    com9 == 1 & year == 2020 ~ 8091591,
    com9 == 1 & year == 2021 ~ 8760986,
    com9 == 1 & year == 2022 ~ 9797691,
    com9 == 1 & year == 2023 ~ 11994355,

    # Villa Alemana (com10)
    com10 == 1 & year == 2018 ~ 4681875,
    com10 == 1 & year == 2019 ~ 4919300,
    com10 == 1 & year == 2020 ~ 4326818,
    com10 == 1 & year == 2021 ~ 5097685,
    com10 == 1 & year == 2022 ~ 6437164,
    com10 == 1 & year == 2023 ~ 8535643,

    # Default case: Assign NA if no condition is met
    TRUE ~ NA_real_
  ))


EOP <- EOP %>%
  mutate(log_ingresos_real = ifelse(ingresos_real > 0,
                                          log(ingresos_real), 
                                          NA))


```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}

EOP$useweb_nona <- replace_na(EOP$useweb, 0)
table(EOP$useweb_nona)

EOP$useadm_nona <- replace_na(EOP$useadm, 0)
table(EOP$useadm_nona)

EOP$useinfo_nona <- replace_na(EOP$useinfo, 0)
table(EOP$useinfo_nona)

EOP$usetransp_nona <- replace_na(EOP$usetransp, 0)
table(EOP$usetransp_nona)

EOP$useother_nona <- replace_na(EOP$useother, 0)
table(EOP$useother_nona)

```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}

cronbach_ope <- alpha(na.omit(EOP[c("ope1", "ope2", "ope3", "ope4")]))
cronbach_ope

cronbach_intpol <- alpha(na.omit(EOP[c("polint1", "polint2", "polint3", "polint4", "polint5")]))
cronbach_intpol

cronbach_use <- alpha(na.omit(EOP[c("useadm_nona", "useinfo_nona", "usetransp_nona", "useother_nona")]))
cronbach_use

EOP_nona <- na.omit(EOP[c("ope1", "ope2", "ope3", "ope4", "dig_mun", "ingresos","log_ingresos_real", "sex", "age", "SES", "education", "polint1", "polint2", "polint3", "polint4", "polint5", "year", "useweb_nona", "useadm_nona", "useinfo_nona", "usetransp_nona", "useother_nona", "mun_id")])

EOP_nona <- EOP_nona %>%
  mutate(across(where(is.labelled), as.numeric))

cfa.model <- 'ope =~ ope1 + ope2 + ope3 + ope4'
cfa.model2 <- 'intpol =~ polint1 + polint2 + polint3 + polint4 + polint5'
cfa.model3 <- 'use =~ useadm_nona + useinfo_nona + usetransp_nona + useother_nona'

fit_cfa <- cfa(cfa.model, data = EOP_nona)
fit_cfa2 <- cfa(cfa.model2, data = EOP_nona)
fit_cfa3 <- cfa(cfa.model3, data = EOP_nona, estimator = "WLSMV")

latent_scores <- predict(fit_cfa)
latent_scores2 <- predict(fit_cfa2)
latent_scores3 <- predict(fit_cfa3)

EOP_nona <- cbind(EOP_nona, latent_scores, latent_scores2, latent_scores3)
```

## Results

**Figure 1** Digital Municipality Index

```{r echo=FALSE, message=FALSE, warning=FALSE}

map1 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = Municipio_Digital, geometry = geometry), color = "transparent", size = 0.5) +
  scale_fill_viridis_c(name = "Services on Website", 
                       option = "C",
                       guide = guide_colorbar(title.position="top")) +
  labs(title = "Digital Municipal Index") +
  theme_map() +
  theme(title = element_text(size = 14, face = "bold", colour = "#000000"),
        legend.title = element_text(size=12, face = "plain", hjust=0.5, lineheight=0.45,        color="black"),
        legend.text=element_text(size=12),
        legend.position = "right",
        legend.direction = "vertical",
        legend.key.width = unit(0.3, "cm"),
        legend.key.height = unit(1, "cm"))
map1

map2 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = log_Poblacion.y, geometry = geometry), color = "transparent", size = 0.5) +
  scale_fill_viridis_c(name = "Population (log)", 
                       option = "C",
                       guide = guide_colorbar(title.position="top")) +
  labs(title = "Population") +
  theme_map() +
  theme(title = element_text(size = 14, face = "bold", colour = "#000000"),
        legend.title = element_text(size=12, face = "plain", hjust=0.5, lineheight=0.45,        color="black"),
        legend.text=element_text(size=12),
        legend.position = "right",
        legend.direction = "vertical",
        legend.key.width = unit(0.3, "cm"),
        legend.key.height = unit(1, "cm"))

map3 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = log_Ingresos_Propios_Permanentes, geometry = geometry), color = "transparent", size = 0.5) +
  scale_fill_viridis_c(name = "Own-source revenues (log)", 
                       option = "C",
                       guide = guide_colorbar(title.position="top")) +
  labs(title = "Municipal Income") +
  theme_map() +
  theme(title = element_text(size = 14, face = "bold", colour = "#000000"),
        legend.title = element_text(size=12, face = "plain", hjust=0.5, lineheight=0.45,        color="black"),
        legend.text=element_text(size=12),
        legend.position = "right",
        legend.direction = "vertical",
        legend.key.width = unit(0.3, "cm"),
        legend.key.height = unit(1, "cm"))

map4 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = share_Planta_Profes, geometry = geometry), color = "transparent", size = 0.5) +
  scale_fill_viridis_c(name = "Workers with degree (%)", 
                       option = "C",
                       guide = guide_colorbar(title.position="top")) +
  labs(title = "Qualified Mun. Workforce") +
  theme_map() +
  theme(title = element_text(size = 14, face = "bold", colour = "#000000"),
        legend.title = element_text(size=12, face = "plain", hjust=0.5, lineheight=0.45,        color="black"),
        legend.text=element_text(size=12),
        legend.position = "right",
        legend.direction = "vertical",
        legend.key.width = unit(0.3, "cm"),
        legend.key.height = unit(1, "cm"))

map5 <- ggplot(data = merged_data) +
  geom_sf(aes(fill = Pob_Rural_Porc, geometry = geometry), color = "transparent", size = 0.5) +
  scale_fill_viridis_c(name = "Population in rural areas (%)", 
                       option = "C",
                       guide = guide_colorbar(title.position="top")) +
  labs(title = "Rural Population") +
  theme_map() +
  theme(title = element_text(size = 14, face = "bold", colour = "#000000"),
        legend.title = element_text(size=12, face = "plain", hjust=0.5, lineheight=0.45,        color="black"),
        legend.text=element_text(size=12),
        legend.position = "right",
        legend.direction = "vertical",
        legend.key.width = unit(0.3, "cm"),
        legend.key.height = unit(1, "cm"))


# Combine maps side by side
combined_maps1 <- map2 + map3 + 
  plot_layout(ncol = 2)

# Plot the combined figure
combined_maps1

# Combine maps side by side
combined_maps2 <- map4 + map5
  plot_layout(ncol = 2)

# Plot the combined figure
combined_maps2

# Save as PNG
ggsave(filename = "combined_maps1.png",          # File name
       plot = combined_maps1,                    # Your combined plot object
       width = 16, height = 12, units = "in",   # Adjust size as you need
       dpi = 300)                                # High resolution for publication

ggsave(filename = "combined_maps2.png",          # File name
       plot = combined_maps2,                    # Your combined plot object
       width = 16, height = 12, units = "in",   # Adjust size as you need
       dpi = 300)                                # High resolution for publication

```

**Figure 2**. Dispersion diagram of the Digital Municipality Index, considering population, rurality, municipal income and quaified municipal workforce.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(merged_data, aes(x = Pob_Rural_Porc, y = Municipio_Digital, size = log_Poblacion.y)) +
  geom_point(alpha = 0.5, color = "darkblue") +
  geom_smooth(method = "lm", color = "#FDE725FF", se = TRUE) +  # Add linear regression line
  labs(title = "Rurality and digitalization",
       x = "Rural Population (%)",
       y = "Digital Municipality Index") +  # Removed size label here as the legend is being removed
  theme_tufte2() +
  scale_size_continuous(range = c(1, 10)) +
  guides(size = FALSE)  # Remove the size legend

ggplot(merged_data, aes(x = log_Ingresos_Propios_Permanentes, y = Municipio_Digital, size = log_Poblacion.y)) +
  geom_point(alpha = 0.5, color = "darkblue") +
  geom_smooth(method = "lm", color = "#FDE725FF", se = TRUE) +  # Add linear regression line
  labs(title = "Municipal incomes and digitalization",
       x = "Municipal Income",
       y = "Digital Municipality Index") +  # Removed size label here as the legend is being removed
  theme_tufte2() +
  scale_size_continuous(range = c(1, 10)) +
  guides(size = FALSE)  # Remove the size legend

ggplot(merged_data, aes(x = share_Planta_Profes, y = Municipio_Digital, size = log_Poblacion.y)) +
  geom_point(alpha = 0.5, color = "darkblue") +
  geom_smooth(method = "lm", color = "#FDE725FF", se = TRUE) +  # Add linear regression line
  labs(title = "Workforce and digitalization",
       x = "Qualified Mun. Workforce (%)",
       y = "Digital Municipality Index") +  # Removed size label here as the legend is being removed
  theme_tufte2() +
  scale_size_continuous(range = c(1, 10)) +
  guides(size = FALSE)  # Remove the size legend

```

**Table 1** OLS for Digital Municipality Index at the municipal level

```{r echo=FALSE, message=FALSE, warning=FALSE}
model0<- lm(Municipio_Digital ~ log_Poblacion.y + Pob_Rural_Porc + log_Ingresos_Propios_Permanentes + share_Planta_Profes, data = merged_data)
summary(model0)

model00 <- lm(Municipio_Digital ~ log_Poblacion.y + Pob_Rural_Porc + log_Ingresos_Propios_Permanentes + share_Planta_Profes + factor(CUTREG), data = merged_data)
summary(model00)

model1 <- lm(Municipio_Digital ~ log_Poblacion.y + Pob_Rural_Porc + log_Ingresos_Propios_Permanentes + share_Planta_Profes, data = md_north)
summary(model1)
model2 <- lm(Municipio_Digital ~ log_Poblacion.y + Pob_Rural_Porc + log_Ingresos_Propios_Permanentes + share_Planta_Profes, data = md_centre)
summary(model2)
model3 <- lm(Municipio_Digital ~ log_Poblacion.y + Pob_Rural_Porc + log_Ingresos_Propios_Permanentes + share_Planta_Profes, data = md_south)
summary(model3)
```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
get_coef <- function(model, model_name) {
  coefs <- summary(model)$coefficients
  data.frame(
    Term = rownames(coefs),
    Estimate = coefs[, "Estimate"],
    Std_Error = coefs[, "Std. Error"],  # Rename to 'Std_Error'
    Model = model_name
  )
}
# Create a mapping of old variable names to new names
name_mapping <- c(
  log_Poblacion.y = "Population (log)",
  Pob_Rural_Porc = "Rural Population (%)",
  log_Ingresos_Propios_Permanentes = "Municipal Income (log)",
  share_Planta_Profes = "Qualified Municipal Workforce (%)"
)
```

**Figure 3**. OLS for Digital Municipality Index at the municipal level

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Assuming coef_df is already prepared as per previous instructions

# Apply the function to both models
coef_df1 <- get_coef(model1, "Model 1")
coef_df2 <- get_coef(model2, "Model 2")
coef_df3 <- get_coef(model3, "Model 3")


# Combine the data frames and remove the intercept
coef_df <- rbind(coef_df1, coef_df2, coef_df3)
coef_df <- coef_df[!coef_df$Term %in% c("(Intercept)"), ]


# Calculate 95% confidence intervals and determine significance
coef_df <- coef_df %>%
  mutate(
    Lower_CI = Estimate - 1.645 * Std_Error,  # Lower bound of the CI
    Upper_CI = Estimate + 1.645 * Std_Error,  # Upper bound of the CI
    Significant = if_else(Lower_CI > 0 & Upper_CI > 0 | Lower_CI < 0 & Upper_CI < 0, TRUE, FALSE)  
    )


# Apply the mapping to the dataframe
coef_df <- coef_df %>%
  mutate(Term = factor(Term, levels = names(name_mapping), labels = name_mapping))

# Define a dodge width for better separation
dodge_width <- 0.5

# Create the plot with updated names
ggplot(coef_df, aes(x = Term, y = Estimate, ymin = Lower_CI, ymax = Upper_CI, color = Model, group = Model)) +
  geom_pointrange(position = position_dodge(width = dodge_width), aes(size = Significant)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "orange") +
  theme_minimal() +
  labs(x = "Variables", y = "Coefficients") +
  coord_flip() +  # Flips the axes for better visualization of terms
  scale_color_manual(values = c("darkblue", "darkred", "darkgreen"),
                     labels = c("Northern Chile", "Central Region of Chile", "Southern Chile")) +  # Set custom colors for each model
  scale_size_manual(values = c(0.5, 1.5), guide = FALSE) +  # Adjust line width based on significance
  theme(
    legend.position = "right",  # Hide the legend for line size
    axis.text.y = element_text(size = 8)  # Adjust text size if needed
  )
```

## Second Part: Analyses at the individual level, Chilean region of Valparaiso as case study

##### INDIVIDUAL ANALYSIS - TO REPORT ##### 
## Testing with real income 2018-2023 and without education

```{r}
modela_mean <- lm(ope ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + factor(year), data = EOP_nona)
#summary(modela_mean)
coeftest(modela_mean, vcov = vcovCR(modela_mean, cluster = EOP_nona$mun_id, type = "CR2"))

modelb_mean <- lm(ope1 ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + factor(year), data = EOP_nona)
#summary(modelb_mean)
coeftest(modelb_mean, vcov = vcovCR(modelb_mean, cluster = EOP_nona$mun_id, type = "CR2"))

modelc_mean <- lm(ope2 ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + factor(year), data = EOP_nona)
#summary(modelc_mean)
coeftest(modelc_mean, vcov = vcovCR(modelc_mean, cluster = EOP_nona$mun_id, type = "CR2"))

modeld_mean <- lm(ope3 ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + factor(year), data = EOP_nona)
#summary(modeld_mean)
coeftest(modeld_mean, vcov = vcovCR(modeld_mean, cluster = EOP_nona$mun_id, type = "CR2"))

modele_mean <- lm(ope4 ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + factor(year), data = EOP_nona)
#summary(modele_mean)
coeftest(modele_mean, vcov = vcovCR(modele_mean, cluster = EOP_nona$mun_id, type = "CR2"))

```

```{r}
modelf_nona_real <- glm(useweb_nona ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona, family = binomial)
#summary(modelf_nona_real)
coeftest(modelf_nona_real, vcov = vcovCR(modelf_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

modelg_nona_real <- glm(useadm_nona ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona, family = binomial)
#summary(modelg_nona_real)
coeftest(modelg_nona_real, vcov = vcovCR(modelg_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

modelh_nona_real <- glm(useinfo_nona ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona, family = binomial)
#summary(modelh_nona_real)
coeftest(modelh_nona_real, vcov = vcovCR(modelh_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

modeli_nona_real <- glm(usetransp_nona ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona, family = binomial)
#summary(modeli_nona_real)
coeftest(modeli_nona_real, vcov = vcovCR(modeli_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

modelj_nona_real <- glm(useother_nona ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona, family = binomial)
#summary(modelj_nona_real)
coeftest(modelj_nona_real, vcov = vcovCR(modelj_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

modelk_nona_real <- lm(use ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + factor(year), data = EOP_nona)
#summary(modelk_nona_real)
coeftest(modelk_nona_real, vcov = vcovCR(modelk_nona_real, cluster = EOP_nona$mun_id, type = "CR2"))

```


## Testing Pandemic Effect ##

```{r}
# Create a binary variable for pre- and post-pandemic
EOP_nona$post_pandemic <- ifelse(EOP_nona$year <= 2020, 0, 1)

modela_pan <- lm(ope ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + post_pandemic, data = EOP_nona)
#summary(modela_pan)
coeftest(modela_pan, vcov = vcovCR(modela_pan, cluster = EOP_nona$mun_id, type = "CR2"))

modela_pan_int1 <- lm(ope ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + post_pandemic + log_ingresos_real * post_pandemic , data = EOP_nona)
#summary(modela_pan_int1)
coeftest(modela_pan_int1, vcov = vcovCR(modela_pan_int1, cluster = EOP_nona$mun_id, type = "CR2"))

modela_pan_int2 <- lm(ope ~ dig_mun + log_ingresos_real + sex + age + SES + intpol + post_pandemic + dig_mun * post_pandemic , data = EOP_nona)
#summary(modela_pan_int2)
coeftest(modela_pan_int2, vcov = vcovCR(modela_pan_int2, cluster = EOP_nona$mun_id, type = "CR2"))


plot1 <- interact_plot(model = modela_pan_int1, pred = "log_ingresos_real", modx = "post_pandemic", 
                       interval = TRUE, x.label = "Income", y.label = "OPE", 
                       modx.labels = c("Pre-Pandemic", "Post-Pandemic"))
plot1

plot2 <- interact_plot(model = modela_pan_int2, pred = "dig_mun", modx = "post_pandemic", 
                       interval = TRUE, x.label = "Digitalised Municipality", y.label = "OPE", 
                       modx.labels = c("Pre-Pandemic", "Post-Pandemic"))
plot2

```

```{r}
modelk_pan <- lm(use ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + post_pandemic, data = EOP_nona)
#summary(modelk_pan)
coeftest(modelk_pan, vcov = vcovCR(modelk_pan, cluster = EOP_nona$mun_id, type = "CR2"))

modela_pan_int3 <- lm(use ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + post_pandemic + log_ingresos_real * post_pandemic , data = EOP_nona)
#summary(modela_pan_int3)
coeftest(modela_pan_int3, vcov = vcovCR(modela_pan_int3, cluster = EOP_nona$mun_id, type = "CR2"))

modela_pan_int4 <- lm(use ~ dig_mun + log_ingresos_real + sex + age + SES + ope + intpol + post_pandemic + dig_mun * post_pandemic , data = EOP_nona)
#summary(modela_pan_int4)
coeftest(modela_pan_int4, vcov = vcovCR(modela_pan_int4, cluster = EOP_nona$mun_id, type = "CR2"))



plot3 <- interact_plot(model = modela_pan_int3, pred = "log_ingresos_real", modx = "post_pandemic", 
                       interval = TRUE, x.label = "Income", y.label = "Use of Mun. Website", 
                       modx.labels = c("Pre-Pandemic", "Post-Pandemic"))
plot3

plot4 <- interact_plot(model = modela_pan_int4, pred = "dig_mun", modx = "post_pandemic", 
                       interval = TRUE, x.label = "Digitalised Municipality", y.label = "Use of Mun. Website", 
                       modx.labels = c("Pre-Pandemic", "Post-Pandemic"))
plot4

```


##### APPENDIX ##### 

